\thetitle

### 2013-04-13 tfpie/tfpie.tex
world programs

\begin{enumerate}
\item Lists of numbers
\item World
\end{enumerate}

>>>>

\begin{figure}
\begin{minipage}[t]{3.4in}
\begin{verbatim}
#lang bsl
(require 2htdp/image 2htdp/universe)

;; A World is a Number

;; on-tick : World -> World
(define (tick w) (add1 w))

;; to-draw : World -> Image
(define (draw w)
  (circle w "solid" "red"))

;; on-key : KeyEvent World -> World
(define (on-key k w) 10)

(big-bang 10
          [to-draw draw]
          [on-tick tick])
\end{verbatim}
\end{minipage}
\begin{minipage}[t]{3in}
\begin{verbatim}
#lang class/1
(require 2htdp/image class/universe)

;; A World (new world% Number)
(define-class world%
  (fields n)
  ;; on-tick : -> World
  (define (on-tick)
    (new world% (add1 (this . n))))
  ;; to-draw : -> Image
  (define (on-tick) 
    (circle (this . n) "solid" "red"))
  ;; on-key : KeyEvent -> World
  (define (on-key k) (new world% 10)))

(big-bang (new world% 10))
\end{verbatim}
\end{minipage}
\caption{World programs}
\label{fig:world}
\end{figure}
